---
title: "Final Presentation"
author: "Danica Butler"
date: "December 19, 2018"
output: ioslides_presentation
---

##Introduction
- This dataset is predicting whether a pitch on the TV Show Shark Tank gets a deal or not
- Helpful to those wishing to go on Shark Tank
- The target variable is "deal", which either true or false.
- Dataset found on Kaggle, added some columns to analyze data
- 22 Variables- most important are the "Asked for" and "Exchanged stake"

##Input Variables
- Name and Description of Product/Service, Category it is in, Website
- Episode/ Season, Air Date
- Entreprenuers Names, Location, Multiple or Not
- $ Asked For, Percent Equity Offered, Valuation of Company
- Sharks Present for Episode

##Input Dataset
```{r}
ST = read.csv("C:/Users/student/Documents/Senior Year/Programming with R/FinalDataset.csv")
library(caret)
library(ggplot2)
```

---
```{r}
library(ggplot2)
ggplot(data = ST) + geom_bar(mapping = aes(x = deal), position = "dodge") + ggtitle("Graph of Target Variable") + labs(fill = "True or False")

```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = AboveAvg), position = "dodge") + ggtitle("Graph of Above or Below Average Ask") + labs(fill = "True or False")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = AboveAvgPer), position = "dodge") + ggtitle("Graph of Above or Below Average Percentage Ask") + labs(fill = "True or False")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = AboveAvg), position = "dodge") + ggtitle("Getting a Deal based on Money Asked For") + labs(fill = "Did they ask for more than 250,000")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = AboveAvgPer), position = "dodge") + ggtitle("Getting a Deal based on Percentage Given") + labs(fill = "Did they Give more than 17.5%?")
```

---
```{r}
ggplot(data = ST) + geom_point(mapping = aes(x = exchangeForStake, y = askedFor/100, color = deal)) + ggtitle("Comparing Money Asked For and Equity Given") + labs(fill = "Accepted A Deal")
```

---
```{r}
ggplot(data = ST) + geom_line(mapping = aes(x = episode, y = valuation/10000, color = deal), position = "dodge") + ggtitle("Trends of Valuation of the Company by Episode")
```

---
```{r}
ggplot(data = ST) + geom_density(mapping = aes(x = valuation/1000)) + ggtitle("Density of Valuation")
```

---
```{r}
ggplot(data = ST) + geom_density(mapping = aes(x = exchangeForStake)) + ggtitle("Density of Exchanged Stake")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = episode, fill = deal), position = "dodge") + ggtitle("Deals per Episode") + labs(fill = "Accepted A Deal")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = season, fill = deal), position = "dodge") + ggtitle("Deals per Season") + labs(fill = "Accepted A Deal")
```

---
```{r}
ggplot(data = ST) + geom_count(mapping = aes(x = MultipleEntreprenuers, y = exchangeForStake, color = deal), position = "dodge") + ggtitle("Percentage Given based on One or More Entreprenuers")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = shark1), position = "dodge") + ggtitle("Deal Based on Shark1") + labs(fill = "Shark")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = shark2), position = "dodge") + ggtitle("Deal Based on Shark2") + labs(fill = "Shark")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = shark3), position = "dodge") + ggtitle("Deal Based on Shark3") + labs(fill = "Shark")
```

---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = shark4), position = "dodge") + ggtitle("Deal Based on Shark4") + labs(fill = "Shark")
```


---
```{r}
ggplot(data = ST) + geom_bar(mapping = aes(x = deal, fill = shark5), position = "dodge") + ggtitle("Deal Based on Shark5") + labs(fill = "Shark")
```


##Handling Missing Values Method 1
- ST$askedFor <- replace(ST$askedFor, ST$askedFor == 0, mode(ST$askedFor))
- This replace missing values in the episode column with the mode of the column.


##Handling Missing Values Method 2
- ST$exchangeForStake <- replace(ST$exchangeForStake, is.na(ST$exchangeForStake), mean(ST$exchangeForStake, na.rm =TRUE))
- This replace missing values in the episode column with the mean of the column.

##Handling Missing Values Method 3
- ST$valuation <- replace(ST$valuation, is.na(ST$valuation), median(ST$valuation, na.rm = TRUE))
- This replace missing values in the episode column with the median of the column.


##Comparing Imputation Methods 
splitIndex <- createDataPartition(ST$deal, p = .70, list = FALSE, times = 1)
train <- ST[splitIndex,]
test <- ST[-splitIndex,]

model <- ranger(deal ~., data = train)
pred <- predict(model, data = test)$predictions
cm <- confusionMatrix(pred, test$deal, positive = "1")
cm

##Results of Confusion Matrix
-Accuracy : 0.473
-95% CI : (0.3904, 0.5566)


##Recoding categorical variables 
```{r}
levels(ST$category) <- c("Food", "Outdoors", "Childrens", "Childrens", "Childrens", "Childrens", "Childrens", "Other", "Fashion", "Fitness", "Other", "Tech", "Tech", "Fashion", "Fitness", "Fitness", "Fitness", "Home", "Outdoors", "Fitness", "Other", "Other", "Home", "Home", "Home", "Home", "Home", "Fashion", "Fashion", "Fashion", "Fashion", "Fashion", "Tech", "Other", "Food", "Other", "Tech", "Outdoors", "Other", "Fashion", "Home", "Home", "Tech", "Other", "Food", "Home", "Childrens", "Fashion", "Food", "Other", "Food", "Fashion", "Fashion", "Fashion")
```



##Predictive Models
##Forest Model
Grid1 = expand.grid(mtry = c(1:2), splitrule = c("gini"),
                     min.node.size = c(1:2))

forest_ST_tuned <- train(deal ~.,data = ST, method = "ranger", 
               trControl = trainControl(method ="cv", number = 7, verboseIter = TRUE),
               tuneGrid = Grid1)
forest_ST_tuned

Accuracy : .507071


##Decision Tree Model
dtree_ST_tuned <- train(deal ~.,data = ST, method = "rpart", 
               trControl = trainControl(method ="cv", number = 10, verboseIter = TRUE))
dtree_ST_tuned

Accuracy : 0.5277119   
cp : 0.01844262  


##Confusion Matrix Model
splitIndex <- createDataPartition(ST$deal, p = .70, list = FALSE, times = 1)
train <- ST[splitIndex,]
test <- ST[-splitIndex,]

model <- ranger(deal ~., data = train)
pred <- predict(model, data = test)$predictions
cm <- confusionMatrix(pred, test$deal, positive = "1")
cm

Accuracy : 0.5338          


##GLMnet Model
Grid2 = expand.grid(.alpha=0:1,.lambda=seq(0.001,1,length=10))


glm_ST = train(deal~., data=ST, method="glmnet")
glm2_ST = train(deal~., data=ST, method="glmnet", tuneGrid = Grid2)
plot(glm_ST)
plot(glm2_ST)
 
